---
title: "Training Peaks"
subtitle: "maxHR Optimization"
author: "[Baker Bioinformatics (Sergio)](https://intranet.baker.edu.au/research-resources/platform-technologies/bioinformatics-program/ )"
date: "`r format(Sys.time(), '%d %B %Y')`"
mail: "bioinformatics@baker.edu.au"
# output:
#   html_notebook:
#     toc: true
#     toc_depth: 3
#     toc_float:
#       collapsed: false
#       smooth_scroll: true
#     theme: cosmo
#     df_print: paged
#     highlight: tango
#     # code_folding: hide
#     # fig_width: 12
#     # fig_height: 12
output:
  epuRate::BAKER:
    toc: TRUE
    number_sections: FALSE
    code_folding: "hide"
---

<script>
$(document).ready(function() {
  $items = $('div#TOC li');
  $items.each(function(idx) {
    num_ul = $(this).parentsUntil('#TOC').length;
    $(this).css({'text-indent': num_ul * 10, 'padding-left': 0});
  });

});
</script>

***

```{r warning=FALSE, results='hide', echo='FALSE', message=FALSE}
# library(fit)
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(ggrepel)
library(foreach)
library(doParallel)
library(zoo)
# library(splines)
# library(openxlsx)
# library(geosphere)
# library(XML)
# library(tidyr)
# library(readr)
```

```{r echo=F}
# supporting functions
smooth.data <- function(data,w){
  sm <- rollapply(data,width=w,function(...) {mean(...,na.rm=T)},partial=T,align="center")
  return(sm)
}

process_maxhr_activity <- function(athid, myact, w_e, w_d, w_x, w_h, nlag = 10, d2f = 0.1) {
  myres <- ggplot_build(ggplot(myact %>% filter(hrmax > 1)) + stat_density(aes(x=hrmax),bw=3))$data[[1]] %>% 
    select(x,y) %>% 
    mutate(ath.id = athid,
           deriv = (y - lag(y))/ (x - lag(x)),
           deriv = smooth.data(deriv, 20),
           # add second derivative as a filter to avoid min/max and focus on slopes (removing all on the bottom and top 10%)
           deriv2 = (deriv - lag(deriv)) / (x - lag(x)),
           score_deriv2 = ifelse(deriv2 < quantile(deriv2, na.rm=T, d2f) | deriv2 > quantile(deriv2, na.rm=T, 1-d2f), 0, 1),
           yinterc = y - x*deriv,
           xinterc = round(-yinterc/deriv,0),
           xinterc = ifelse(is.na(xinterc) | !is.finite(xinterc),999,xinterc), # fix errors in xinterc exactly 0
           xinterc_diff = xinterc - lag(xinterc, default = 0, n = nlag)) %>% 
    rowwise() %>% 
    mutate(error_act = sum(myact$hrmax > xinterc),
           error_perc = sum(myact$hrmax > xinterc)/length(myact$hrmax) * 100,
           error_perc5 = ifelse(error_perc > 5, error_perc, 0)
    ) %>% 
    ungroup() %>% 
    mutate(rank_error = dense_rank(error_act * error_perc), 
           # better to have a scaled score instead of a ranked normalization
           # substract 5% to error_perc so we don't mind if there is 5% error --> no difference
           score_error = scale(error_act * (error_perc5)) + abs(min(scale(error_act * (error_perc5)), na.rm=T)),
           score_error_perc = scale(error_perc5) + abs(min(scale(error_perc5), na.rm=T)),
           rank_deriv = dense_rank(desc(deriv)),
           # same with derivative, no point on ranking, better to leave it scaled as it is
           score_deriv = scale(-deriv),
           # score_deriv2 = scale(deriv2),
           # the "xintercdiff" is a bit tricky, as I implemented it to avoid correcting high error rates by going to flat derivative
           # this way, if the section of the curve is a highly variable one, such as maximums or minimums, it gets penalized
           # I will also score is as a scale
           rank_xintercdiff = dense_rank(abs(xinterc_diff)),
           score_xintercdiff = ifelse(abs(xinterc_diff) < 3,
                                 scale(abs(xinterc_diff)) + abs(min(scale(abs(xinterc_diff)), na.rm=T)),
                                 abs(xinterc_diff)))
  # NEW THING, after the nice optimization, some athletes were prioritizing the late and small peaks
  # to correct for that, I will create a "highness" measure, so higher peaks are prioritized
  # first, find local maxs
  loc_max <- myres %>% filter(deriv * lag(deriv) < 0 & deriv2 < 0) %>% 
    mutate(y = ifelse(x < 140, y[y!=max(y)]*1.1,y)) # correct for way too big peaks before 140... artifacts
  loc_inflex <- myres %>% filter(deriv2 * lag(deriv2) < 0 | row_number() == n())
  # now, create a new column with highness value
  myres <- myres %>% 
    rowwise() %>% 
    mutate(highness = loc_max$y[last(which(loc_max$x < x))],
           score_error = ifelse(length(myact$hrmax) < 100,
                                score_error / 15,
                                ifelse(length(myact$hrmax) < 200,
                                       score_error / 5,
                                       score_error)),
           # add inflexion points (some plots with inflex points at the end are giving errors)
           score_deriv2 = ifelse(any(x < (loc_inflex$x + 1) & x > (loc_inflex$x - 1)),
                                 1, score_deriv2)
    ) %>% 
    ungroup() %>% 
    mutate(highness = scale(highness**3) + abs(min(scale(highness**3), na.rm=T)),
           score_highness = case_when(is.na(highness) ~ 0,
                                      highness == 0 ~ 0.1,
                                      TRUE ~ highness / 5),
           optim = (-score_error * w_e + score_deriv * w_d - score_xintercdiff * w_x + score_highness * w_h),
           optim = ifelse(xinterc > 230, NA, optim), # fix for way too high xinterc
           optim = ifelse(x < 140 & xinterc > 200, NA, optim), # fix for wrongly found x, before 140
           optim = ifelse(deriv > 0, NA, optim), # to remove "going up" slopes
           optim = ifelse(score_deriv2 == 0, NA, optim), # last one, to apply score_deriv filter
    )
  
  return(myres)
}

plot_maxhrall_test <- function(maxhr_all, optim_zoom=20000) {
  anno <- maxhr_all %>%
    group_by(ath.id) %>%
    arrange(-optim) %>%
    filter(row_number() == 1) %>%
    left_join(maxhr_values, by = "ath.id")

  p <- ggplot(maxhr_all,aes(x=x)) +
    # ylim(c(-0.03,0.05)) +
    scale_y_continuous(limits = c(-0.03, NA)) +
    xlim(c(120, 250)) +
    geom_line(aes(y=y), col="black", size=2) +
    geom_line(aes(y=score_deriv/80), col="red", size=1) +
    geom_line(aes(y=deriv2*50), col="darkred", size=1) +
    geom_line(aes(y=score_deriv2/50), col="maroon", size=1) +
    # geom_line(aes(y=-deriv*5), col="red", size=1) +
    # geom_line(aes(y=xinterc/20000), col="blue") +
    # geom_line(aes(y=score_xintercdiff/60), col="orange", size=1) +
    # geom_line(aes(y=error_perc/4000), col="purple", size=2) +
    # geom_line(aes(y = (rank_error + rank_deriv + rank_xintercdiff)/30000), col="green", size=1.5) +
    geom_line(aes(y=score_error/60), col="purple", size=1) +
    geom_line(aes(y=optim/optim_zoom), col = "darkgreen", size=2) +
    facet_wrap(~ ath.id) +
    # geom_hline(data = anno,
    #              aes(yintercept = q10*50, col="q10"), size = 1.5) +
    # geom_hline(data = anno,
    #              aes(yintercept = q05*50, col="q05"), size = 1.5) +
    # geom_hline(data = anno,
    #              aes(yintercept = q15*50, col="q15"), size = 1.5) +
    # geom_hline(data = anno,
    #              aes(yintercept = q20*50, col="q20"), size = 1.5) +
    geom_segment(data=anno,
                 aes(x=x,y=y,xend=xinterc,yend=0),color="blue",size=1.4) +
    geom_text(data = anno,
              aes(label=xinterc, x=xinterc, y=0), hjust=0, color="blue", cex=12) +
    geom_text(data = anno,
              aes(label=ideal, x=200, y=y), hjust=0, color="red", cex=12)
  return(p)
}
```


*** 

# All athletes

## Get files and load

```{r}
optim_files <- Sys.glob("all/optim*.rda")
for (myfile in optim_files) {
  load(myfile)
}
```

## Load ideal maxHR (manual)

I manually checked every plot and saved the "ideal" result, so we can train a model to find the best parameters with the best outcome.

```{r}
# I manually checked every plot and saved the ideal result, so we can train and test the best parameters
# all_files <- Sys.glob('all/optim*rda')
load("maxhr_values_reference.rda")
maxhr_values[maxhr_values$ath.id == "BA_096","ideal"] <- 154
maxhr_values[maxhr_values$ath.id == "BA_109","ideal"] <- 162
maxhr_values[maxhr_values$ath.id == "BA_139","ideal"] <- 144
# maxhr_values[maxhr_values$ath.id == "BA_084","ideal"] <- 182
maxhr_values[maxhr_values$ath.id == "BA_125","ideal"] <- 163
maxhr_values[maxhr_values$ath.id == "BA_036","ideal"] <- 195
# maxhr_values[maxhr_values$ath.id == "BA_151","ideal"] <- 168
maxhr_values[maxhr_values$ath.id == "BA_105","ideal"] <- 145
maxhr_values[maxhr_values$ath.id == "BA_110","ideal"] <- 175
maxhr_values[maxhr_values$ath.id == "BA_122","ideal"] <- 183
maxhr_values[maxhr_values$ath.id == "BA_051","ideal"] <- 168
maxhr_values[maxhr_values$ath.id == "BA_146","ideal"] <- 186
maxhr_values %>% select(-name)
```

## Calculate maxHR for everyone

```{r fig.width=12, warning=F, echo = F}
maxhr_all <- NULL
optim_files <- Sys.glob("all/optim*rda")
# sel_athletes <- 
sel_athletes <- c(1,2, 11, 13, 94, 116, 96, 88, 115, 151, 73, 122, 99, 78, 27)
sel_athletes.code <- paste0("BA_",str_pad(sel_athletes,3,pad="0"))
optim_files <- optim_files[grepl(paste0(sel_athletes.code, collapse = "|"), optim_files)]
w_e <- 80
w_d <- 1
w_x <- 4
w_h <- 0
nlag <- 10
d2f <- 0.2
# optim_files <- optim_files[c(1,2,11,19)]
# optim_files <- optim_files[c(11,14)]

for (myfile in optim_files) {
  # load(myfile)
  # get athlete code from file, and save variable name to call later
  athid <- str_remove(str_split(str_remove(myfile, "all/"),"\\.")[[1]][1],"optim_maxhr_act_")
  varname <- paste0("maxhr_act_",str_remove(str_split(str_remove(myfile, "all/"),"\\.")[[1]][1],"optim_maxhr_act_"))
  # get plot data to calculate derivative et al
  tmp <- ggplot_build(ggplot(get(varname) %>% filter(hrmax > 1)) + stat_density(aes(x=hrmax),bw=3))$data[[1]] %>% 
    select(x,y) %>%
    mutate(ath.id = athid,
           deriv = (y - lag(y)) / (x - lag(x)),
           deriv = smooth.data(deriv, 20),
           deriv2 = (deriv - lag(deriv)) / (x - lag(x)),
           score_deriv2 = ifelse(deriv2 < quantile(deriv2, na.rm=T, d2f) | deriv2 > quantile(deriv2, na.rm=T, 1-d2f), 0, 1),
           yinterc = y - x*deriv,
           xinterc = round(-yinterc/deriv,0),
           xinterc = ifelse(is.na(xinterc) | !is.finite(xinterc),999,xinterc),
           xinterc_diff = xinterc - lag(xinterc, default = 0, n=nlag)) %>% 
    rowwise() %>% 
    mutate(error_act = sum(get(varname)$hrmax > xinterc),
           error_perc = sum(get(varname)$hrmax > xinterc)/length(get(varname)$hrmax) * 100,
           error_perc5 = ifelse(error_perc > 5, error_perc, 0)
    ) %>% 
    ungroup() %>% 
    mutate(
      # rank_error = dense_rank(error_act * error_perc), 
      # better to have a scaled score instead of a ranked normalization
      # substract 5% to error_perc so we don't mind if there is 5% error --> no difference
      score_error = scale(error_act * (error_perc5)) + abs(min(scale(error_act * (error_perc5)), na.rm=T)),
      score_error_perc = scale(error_perc5) + abs(min(scale(error_perc5), na.rm=T)),
      # rank_deriv = dense_rank(desc(deriv)),
      # same with derivative, no point on ranking, better to leave it scaled as it is
      score_deriv = scale(-deriv),
      # the "xintercdiff" is a bit tricky, as I implemented it to avoid correcting high error rates by going to flat derivative
      # this way, if the section of the curve is a highly variable one, such as maximums or minimums, it gets penalized
      # I will also score is as a scale
      # rank_xintercdiff = dense_rank(abs(xinterc_diff)),
      score_xintercdiff = ifelse(abs(xinterc_diff) < 3,
                                 scale(abs(xinterc_diff)) + abs(min(scale(abs(xinterc_diff)), na.rm=T)),
                                 abs(xinterc_diff)))
  # NEW THING, after the nice optimization, some athletes were prioritizing the late and small peaks
  # to correct for that, I will create a "highness" measure, so higher peaks are prioritized
  # first, find local maxs
  loc_max <- tmp %>% filter(deriv * lag(deriv) < 0 & deriv2 < 0) %>% 
    mutate(y = ifelse(x < 140, y[y!=max(y)]*1.1,y)) # correct for way too big peaks before 140... artifacts
  loc_inflex <- tmp %>% filter(deriv2 * lag(deriv2) < 0 | row_number() == n())
  # now, create a new column with highness value
  tmp <- tmp %>% 
    rowwise() %>% 
    mutate(highness = loc_max$y[last(which(loc_max$x < x))],
           score_error = ifelse(length(get(varname)$hrmax) < 100,
                                score_error / 15,
                                ifelse(length(get(varname)$hrmax) < 200,
                                       score_error / 5,
                                       score_error)),
           # add inflexion points (some plots with inflex points at the end are giving errors)
           score_deriv2 = ifelse(any(x < (loc_inflex$x + 1) & x > (loc_inflex$x - 1)),
                                 1, score_deriv2)
           ) %>% 
    ungroup() %>% 
    mutate(highness = scale(highness**3) + abs(min(scale(highness**3), na.rm=T)),
           score_highness = case_when(is.na(highness) ~ 0,
                                      highness == 0 ~ 0.1,
                                      TRUE ~ highness / 5),
           optim = (-score_error * w_e + score_deriv * w_d - score_xintercdiff * w_x + score_highness * w_h),
           optim = ifelse(xinterc > 230, NA, optim), # fix for way too high xinterc
           optim = ifelse(x < 140 & xinterc > 200, NA, optim), # fix for wrongly found x, before 140
           optim = ifelse(deriv > 0, NA, optim), # to remove "going up" slopes
           optim = ifelse(score_deriv2 == 0, NA, optim), # last one, to apply score_deriv filter
    )
  maxhr_all <- rbind(maxhr_all,tmp)
}
# maxhr_all <- maxhr_all %>% drop_na()
anno <- maxhr_all %>% 
  group_by(ath.id) %>% 
  arrange(-optim) %>% 
  filter(row_number() == 1) %>%
  left_join(maxhr_values, by = "ath.id")
# anno
```

### Current situation

* Easy case

```{r fig.width=6, warning=F}
# plot_maxhrall_test(maxhr_all, optim_zoom=1000)
testid <- "BA_001"
# maxhr_all %>% filter(ath.id == testid)
ggplot(maxhr_all %>% filter(ath.id == testid) %>% mutate(score_error = ifelse(score_error > 1, NA, score_error)), aes(x=x)) +
  # ylim(c(-2,2)) +
  geom_line(aes(y=y*30)) +
  # geom_line(aes(y=deriv2*100, col="deriv2")) +
  # geom_line(aes(y=optim/1000, col="optim"), size=1.5) +
  # geom_line(aes(y=score_highness, col="highness"), size=2) +
  geom_line(aes(y=score_deriv/10, col="Derivative")) +
  labs(y="Density", x="HR (bpm)", col="") +
  theme_bw()

  # geom_line(aes(y=-score_error*5, col="score_error")) +
  # geom_line(aes(y=xinterc_diff/40000, col="xintercdiff")) +
  # geom_line(aes(y=score_deriv2, col="deriv2"))
# maxhr_all %>% filter(ath.id == testid) %>% arrange(-optim) %>% mutate(n=row_number()) %>% group_by(xinterc) %>%
# filter(row_number() == 1)
```

* What about here?

```{r fig.width=6, warning=F}
# plot_maxhrall_test(maxhr_all, optim_zoom=1000)
testid <- "BA_115"
# maxhr_all %>% filter(ath.id == testid)
ggplot(maxhr_all %>% filter(ath.id == testid) %>% mutate(score_error = ifelse(score_error > 1, NA, score_error)), aes(x=x)) +
  # ylim(c(-2,2)) +
  geom_line(aes(y=y*30)) +
  # geom_line(aes(y=deriv2*100, col="deriv2")) +
  # geom_line(aes(y=optim/1000, col="optim"), size=1.5) +
  # geom_line(aes(y=score_highness, col="highness"), size=2) +
  geom_line(aes(y=score_deriv/10, col="Derivative")) +
  labs(y="Density", x="HR (bpm)", col="") +
  theme_bw()
  # geom_line(aes(y=-score_error*5, col="score_error")) +
  # geom_line(aes(y=xinterc_diff/40000, col="xintercdiff")) +
  # geom_line(aes(y=score_deriv2, col="deriv2"))
# maxhr_all %>% filter(ath.id == testid) %>% arrange(-optim) %>% mutate(n=row_number()) %>% group_by(xinterc) %>%
# filter(row_number() == 1)
```

### New optimization function

* Easy case

```{r fig.width=6, warning=F}
# plot_maxhrall_test(maxhr_all, optim_zoom=1000)
testid <- "BA_001"
# maxhr_all %>% filter(ath.id == testid)
ggplot(maxhr_all %>% filter(ath.id == testid), aes(x=x)) +
  ylim(c(-0.5,0.7)) +
  geom_line(aes(y=y*30)) +
  # geom_line(aes(y=deriv2*100, col="deriv2")) +
  # geom_line(aes(y=optim/1000, col="optim"), size=1.5) +
  # geom_line(aes(y=score_highness, col="highness"), size=2) +
  geom_line(aes(y=score_deriv/10, col="Derivative")) +
  geom_line(aes(y=error_perc/200, col="Error")) +
  labs(y="Density", x="HR (bpm)", col="") +
  theme_bw()

# maxhr_all %>% filter(ath.id == testid)
  # geom_line(aes(y=-score_error*5, col="score_error")) +
  # geom_line(aes(y=xinterc_diff/40000, col="xintercdiff")) +
  # geom_line(aes(y=score_deriv2, col="deriv2"))
# maxhr_all %>% filter(ath.id == testid) %>% arrange(-optim) %>% mutate(n=row_number()) %>% group_by(xinterc) %>%
# filter(row_number() == 1)
```

* Hard case

```{r fig.width=6, warning=F}
# plot_maxhrall_test(maxhr_all, optim_zoom=1000)
testid <- "BA_115"
# maxhr_all %>% filter(ath.id == testid)
ggplot(maxhr_all %>% filter(ath.id == testid), aes(x=x)) +
  ylim(c(-0.5,0.9)) +
  geom_line(aes(y=y*30)) +
  # geom_line(aes(y=deriv2*100, col="deriv2")) +
  # geom_line(aes(y=optim/1000, col="optim"), size=1.5) +
  # geom_line(aes(y=score_highness, col="highness"), size=2) +
  geom_line(aes(y=score_deriv/10, col="Derivative")) +
  geom_line(aes(y=error_perc/200, col="Error")) +
  labs(y="Density", x="HR (bpm)", col="") +
  theme_bw()

# maxhr_all %>% filter(ath.id == testid)
  # geom_line(aes(y=-score_error*5, col="score_error")) +
  # geom_line(aes(y=xinterc_diff/40000, col="xintercdiff")) +
  # geom_line(aes(y=score_deriv2, col="deriv2"))
# maxhr_all %>% filter(ath.id == testid) %>% arrange(-optim) %>% mutate(n=row_number()) %>% group_by(xinterc) %>%
# filter(row_number() == 1)
```

### Optimized function

* Easy case

```{r fig.width=6, warning=F}
# plot_maxhrall_test(maxhr_all, optim_zoom=1000)
testid <- "BA_001"
# maxhr_all %>% filter(ath.id == testid)
ggplot(maxhr_all %>% filter(ath.id == testid), aes(x=x)) +
  ylim(c(-0.5,0.7)) +
  geom_line(aes(y=y*30)) +
  # geom_line(aes(y=deriv2*100, col="deriv2")) +
  # geom_line(aes(y=score_highness, col="highness"), size=2) +
  geom_line(aes(y=score_deriv/10, col="Derivative")) +
  geom_line(aes(y=error_perc/200, col="Error")) +
  geom_line(aes(y=optim/50 + 0.25, col="Optim score"), size=1.2) +
  labs(y="Density", x="HR (bpm)", col="") +
  theme_bw()

# maxhr_all %>% filter(ath.id == testid)
  # geom_line(aes(y=-score_error*5, col="score_error")) +
  # geom_line(aes(y=xinterc_diff/40000, col="xintercdiff")) +
  # geom_line(aes(y=score_deriv2, col="deriv2"))
# maxhr_all %>% filter(ath.id == testid) %>% arrange(-optim) %>% mutate(n=row_number()) %>% group_by(xinterc) %>%
# filter(row_number() == 1)
```

* Hard case

```{r fig.width=6, warning=F}
testid <- "BA_115"
ggplot(maxhr_all %>% filter(ath.id == testid), aes(x=x)) +
  ylim(c(-0.5,0.9)) +
  geom_line(aes(y=y*30)) +
  geom_line(aes(y=score_deriv/10, col="Derivative")) +
  geom_line(aes(y=error_perc/200, col="Error")) +
  geom_line(aes(y=optim/50 + 0.25, col="Optim score"), size=1.2) +
  labs(y="Density", x="HR (bpm)", col="") +
  theme_bw()
```

# Optimization

## Fitness function

This function calculates all the maxHR for all the athletes and compares the results with the manual "ideal" values defined before.

It then returns a fitness value proportional to the difference in predicted/ideal for each of the athletes. The lower this value, the better fitness it is. 

```{r}
fitness_f <- function(w_error = 70, w_deriv = 1, w_xintercdiff = 10, w_highness = 0, nlag = 10, d2f = 0.2, plot = 0, debug=0) {
  optim_files <- Sys.glob("all/wrist*rda")
  # optim_files <- optim_files[c(1,2,14,20)]
  maxhr_all <- NULL
  real_chest_brand <- c("srm", "zwift", "giant_manufacturing_co",
                      "bryton", "stages_cycling")
  for (myfile in optim_files) {
    athid <- str_remove(str_split(str_remove(myfile, "all/"),"\\.")[[1]][1],"wrist_maxhr_act_")
    varname <- paste0("maxhr_act_", str_remove(str_split(str_remove(myfile, "all/"), "\\.")[[1]][1], "wrist_maxhr_act_"))
    myact <- get(varname) %>% 
      filter(hrmax > 1) %>% 
      mutate(hr.sensor = ifelse(device_brand %in% real_chest_brand, TRUE, hr.sensor)) %>% 
      mutate(hr.sensor = ifelse(grepl("edge_", device_model), TRUE, hr.sensor)) %>% 
      filter(hr.sensor == TRUE)
    # if wrist is more than 70%, do not remove them
    if((dim(myact)[1] / dim(get(varname))[1]) < 0.3 | dim(myact)[1] < 10){
      myact <- get(varname) %>% 
        filter(hrmax > 1) %>% 
        mutate(hr.sensor = ifelse(device_brand %in% real_chest_brand, TRUE, hr.sensor)) %>% 
        mutate(hr.sensor = ifelse(grepl("edge_", device_model), TRUE, hr.sensor))
    }
    tmp <- process_maxhr_activity(athid, get(varname), w_error, w_deriv, w_xintercdiff, w_highness, nlag, d2f)
    maxhr_all <- rbind(maxhr_all,tmp)
    maxhr_all <<- maxhr_all
    # maxhr_all <<- maxhr_all %>% drop_na()
  }
  # theo <- setNames(data.frame(maxhr_all %>% pull(ath.id) %>% unique()), "ath.id")
  theo <- maxhr_all %>% 
    group_by(ath.id) %>% 
    arrange(-optim) %>% 
    # filter(optim_rank ==1) %>% 
    filter(row_number() == 1) %>% 
    select(ath.id, predicted=xinterc)
  theo <- left_join(theo, maxhr_values, by="ath.id") %>% select(ath.id, predicted, ideal)
  if (debug == 1) {
    print(theo %>% mutate(diff = abs(ideal-predicted)) %>% arrange(-diff)) # debug
  }
  if (plot == 1) {
    p <- ggplot(theo) +
      geom_point(aes(x=ideal, y=predicted)) +
      geom_text_repel(aes(x=ideal, y=predicted,
                          label=ifelse(abs(ideal - predicted) > 2, paste0(ath.id,": ", predicted, " (", ideal,")"), "")),
                      box.padding = 0.5) +
      # coord_fixed() +
      labs(title=paste0("maxHR fitness with: W(e) = ", w_error ,", W(d) = ", w_deriv ,", W(x) = ", w_xintercdiff),
           subtitle=paste0("MAE: ", sum(abs(theo$ideal - theo$predicted))),
           x="Ideal maxHR (bpm)", y="Predicted maxHR(bpm)") +
      theme(aspect.ratio=1) +
      xlim(c(min(as.numeric(unlist(theo[,c(2,3)])), na.rm=T),
             max(as.numeric(unlist(theo[,c(2,3)])), na.rm=T))) +
      ylim(c(min(as.numeric(unlist(theo[,c(2,3)])), na.rm=T),
             max(as.numeric(unlist(theo[,c(2,3)])), na.rm=T)))
    return(p)
  }
  # calculate MAE
  return(sum(abs(theo$ideal - theo$predicted), na.rm=T))
}
```


```{r warning = F, fig.width=6, fig.height=6}
p <- fitness_f(w_error = 1, w_deriv = 1, w_xintercdiff = 1,  w_highness = 0, nlag = 10, d2f = 0.2, plot = 1, debug = 0)
p
```


## Run grid optimization

```{r warning=F}
res <- NULL
start <- Sys.time()
w2 <- 1
for (w1 in c(1,10)) {
  for (w3 in c(0,1)){
    res <- rbind(res, setNames(data.frame(matrix(c(w1, w2, w3, fitness_f(w1, w2, w3)), nrow=1)), c("we", "wd", "wx", "fitness")))
    # print(res)
  }
}
end <- Sys.time()
duration <- end-start
print(duration)
knitr::kable(res)
```

### Evolution

```{r warning = F, fig.width=12, fig.height=6}
p1 <- fitness_f(w_error = 1, w_deriv = 1, w_xintercdiff = 0,  w_highness = 0, nlag = 10, d2f = 0.2, plot = 1, debug = 0)
p2 <- fitness_f(w_error = 10, w_deriv = 1, w_xintercdiff = 1,  w_highness = 0, nlag = 10, d2f = 0.2, plot = 1, debug = 0)
cowplot::plot_grid(p1,p2)
```


# Final selection

Running this over hundreds of thousands of combinations, we can find the best option for each parameter:

```{r warning = F, fig.width=6, fig.height=6}
p <- fitness_f(w_error = 80, w_deriv = 1, w_xintercdiff = 4,  w_highness = 0, nlag = 10, d2f = 0.2, plot = 1, debug = 0)
p
```

```{r warning=F, fig.width=6, fig.height=8}
cowplot::plot_grid(plot_maxhrall_test(maxhr_all %>% filter(ath.id == "BA_116")),
                   plot_maxhrall_test(maxhr_all %>% filter(ath.id == "BA_151")), nrow=2)
```


